Matching Bullets

### 2015-12-02 imaging-paper.Rnw
adding the old results for comparison
'stable' crosscuts

\subsection{Varying crosscuts}
The crosscut at which a comparison is done matters -- as crosscuts are further apart, more pronounced differences between the crosscuts show up. For bullet land 1-5 from barrel 1 crosscuts at intervals of 50$\mu m$ between 150$\mu m$  and 450$\mu m$  are compared to a crosscut at 100$\mu m$. The initially almost perfect match (consolidated by a CMS of nineteen) between the  crosscuts deteriorates with increasing distance to a very questionable match at $x = 350\mu m$ and non-matches further apart. Only if the crosscut is within 200$\mu m$ do we get a good visual match. Given that alignment in the microscope is not perfect, we should take this into account in the automatic matching routine by evaluating matches at several cross sections. \hh{XXX We're not doing that yet, but it might help - particular for bullets that have larger break-offs at the bottom.}
\begin{figure}
<<crosscuts-vary, echo=FALSE, fig.width = 7, fig.height = 14, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100, 450, by = 50)
lof <- processBullets(paths[5], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

\hh{XXX Does this give us a way to automatically check for the bottom of the bullet? Attempt below} 
By comparing cross sections that are not too far apart -- maybe 25 or 50 $\mu m$ for example -- we get an indication whether the crosscut is in a rapidly changing section, such as in a break-off, or in a stable section, where we can expect to find matches reasonably well. In the approach here, we choose a slightly higher crosscut until we find a section with a stable pattern. This process is shown  in Figure~\ref{fig:crosscuts2} at the example of land 1-1 from barrel 3.

\begin{figure}
<<crosscuts-vary-b31, echo=FALSE, fig.width = 7, fig.height = 10, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100,225, by=25)
lof <- processBullets(paths[37], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

\hh{We can use the Hamby study to run all unkowns against the known bullets. When things go perfectly, they look like in Figure~\ref{fig:hamby-perfect}.}

@@

@
\end{subfigure}
\caption{\label{fig:hamby-perfect}Showcase scenario  when matching with CMS works perfectly. Unfortunately the matches are not always that convincing.}
\end{figure}

\section{Evaluation}
\hh{XXX a lot more about the Hamby study. Fifteen unknown bullets (i.e. 90 lands) compared to two times ten known bullets (i.e. 120 lands) makes $90 \times 120 = 10,800$ land to land comparisons, out of which 180 are actual matches. It is not reasonable to assume that we can match all lands, but we can try to maximize the number of matches. }
Figure~\ref{fig:cms} shows the strong connection between the maximal number of consecutive striae and matches in the Hamby study. All 28 pairs of lands with at least nine CMS in common are matches. For smaller number of CMS, the percentage of false positives quickly increases. 
\begin{figure}
\begin{subfigure}[t]{\linewidth}
\caption{Distribution of maximal CMS.}
<<cms-bars, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
bstats <- read.csv("data/bullet-stats.csv")
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms))) + theme_bw() +
  theme(legend.position="bottom") + 
  xlab("maximum CMS")
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{All bullet pairs with a maximum of at least nine CMS are matches.}
<<cms-spines, echo=FALSE,  fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
bstats <- read.csv("data/bullet-stats.csv")
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms), fill=match), position="fill") +
  theme(legend.position="bottom") + 
  xlab("maximum CMS")
@
\end{subfigure}
\caption{\label{fig:cms}Overview of the maximal number of consecutive maximal striae compared to matches.}
\end{figure}

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{references}

>>>>

\subsection{Varying crosscuts}
The crosscut at which a comparison is done matters -- as crosscuts are further apart, more pronounced differences between the crosscuts show up. For bullet land 1-5 from barrel 1 crosscuts at intervals of 50$\mu m$ between 150$\mu m$  and 450$\mu m$  are compared to a crosscut at 100$\mu m$. The initially almost perfect match (consolidated by a CMS of nineteen) between the  crosscuts deteriorates with increasing distance to a very questionable match at $x = 350\mu m$ and non-matches further apart. Only if the crosscut is within 200$\mu m$ do we get a good visual match. Given that alignment in the microscope is not perfect, we should take this into account in the automatic matching routine by evaluating matches at several cross sections. 
\begin{figure}
<<crosscuts-vary, echo=FALSE, fig.width = 7, fig.height = 14, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100, 450, by = 50)
lof <- processBullets(paths[5], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

%\hh{XXX Does this give us a way to automatically check for the bottom of the bullet? Attempt below} 
By comparing cross sections that are not too far apart -- maybe 25 or 50 $\mu m$ for example -- we get an indication whether the crosscut is in a rapidly changing section, indicative of a break-off, or in a stable section, where we can expect to find matches reasonably well. In the approach here, we keep increasing the crosscut level until we find a section with a stable pattern. This process is shown  in Figure~\ref{fig:crosscuts2} at the example of land 1-1 from barrel 3.
\hh{`Stability' is here defined as two aligned crosscuts chosen 12.5$\mu m$ apart having a cross-correlation of at least 0.9. }
\begin{figure}
<<crosscuts-vary-b31, echo=FALSE, fig.width = 7, fig.height = 10, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100,225, by=25)
lof <- processBullets(paths[37], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

\section{Evaluation}

\hh{We can use the Hamby study to run all unkowns against the known bullets. When things go perfectly, they look like the results in Figure~\ref{fig:hamby-perfect}.}

@@

@
\end{subfigure}
\caption{\label{fig:hamby-perfect}Showcase scenario  when matching with CMS works perfectly. Unfortunately the matches are not always that convincing.}
\end{figure}
\hh{XXX a lot more about the Hamby study. Fifteen unknown bullets (i.e. 90 lands) compared to two times ten known bullets (i.e. 120 lands) makes $90 \times 120 = 10,800$ land to land comparisons, out of which 180 are actual matches. It is not reasonable to assume that we can match all lands, but we can try to maximize the number of matches. }
Figure~\ref{fig:cms} shows the strong connection between the maximal number of consecutive striae and matches in the Hamby study. All 28 pairs of lands with at least nine CMS in common are matches. For smaller number of CMS, the percentage of false positives quickly increases. 
\begin{figure}
\begin{subfigure}[t]{\linewidth}
\caption{Distribution of maximal CMS.}
<<cms-bars, echo=FALSE, fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
bstats <- read.csv("data/bullet-stats.csv")
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms))) + theme_bw() +
  theme(legend.position="bottom") + 
  xlab("maximum CMS")
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{All bullet pairs with a maximum of at least nine CMS are matches.}
<<cms-spines, echo=FALSE,  fig.width=7, fig.height=3.5, out.width='\\linewidth'>>=
bstats <- read.csv("data/bullet-stats.csv")
ggplot(data=bstats) + 
  geom_bar(aes(x=factor(cms), fill=match), position="fill") +
  theme(legend.position="bottom") + 
  xlab("maximum CMS")
@
\end{subfigure}
\caption{\label{fig:cms}Overview of the maximal number of consecutive maximal striae compared to matches.}
\end{figure}

@@

\hh{Things we discussed}
\begin{enumerate}
\item adding more non-matches into the mix is going to make things more realistic. 
\end{enumerate}
\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{references}
